Models of lens candidates from Space Warps CFHTLS

### 2017-03-22 parts/intro.tex
small edits

By coincidence, the typical escape velocity of massive galaxies is
such that $v_{\rm esc}^2/c^2$ is comparable to the apparent sizes of a
galaxies at cosmological distances.  This coincidence is fortunate,
because it makes the lensing deflection angle (which is $2v_{\rm
  esc}^2/c^2$) of distant galaxies comparable to their size on the
sky, and as a result, strong lensing by galaxies tends to produce
images that probe the dark halos of those galaxies.  This is
important, because while there is a general consensus that basic
mechanism of galaxy formation involve gravitational collapse,
fragmentation, and mergers of dark-matter clumps, into which gas fell,
cooling through radiative processes to form dense clouds and
eventually stars, there is much debate about the details \citep[for a
  summary, see][]{2012RAA....12..917S}.  In particular, the nature of
dark matter remains mysterious: most researchers take it to be a
collisionless non-relativistic fluid (cold dark matter or CDM) readily
studied by simulations \citep[for example, the millenium simulation
  by][which has been particularly influential]{2005Natur.435..629S}.
But other scenarios have also been considered, such as a cold
condensing boson fluid \citep{2016ApJ...818...89S}, or dark matter
particles with internal degrees of freedom
\citep{2010MNRAS.405...77S}, or not matter at all but a modification
of gravity \citep{2016PhRvL.117t1101M}.

@@

This paper continues by applying SpaghettiLens to lens-candidates
discovered through Space~Warps.  We present results from modelling of
42 of the 59 lens candidates reported by \cite{2016MNRAS.455.1191M}.
Each lens candidate was modelled in a collaborative refinement
process, where anyone interested can create a new model or modify an
existing model to try and make it better.\footnote{This is in contrast
  to the main Space~Warps project for discovering lenses, where
  volunteers in a crowd of $\gtrsim10^4$ make independent
  contributions.  Each person is presented with a random selection of
  survey-patches and invited to (in effect) vote on each.  The system
  estimates each volunteer's skill level according to test-patches
  interspersed with the real data, and weights their votes accordingly
  \citep{2016MNRAS.455.1171M}.  There is an active forum for
  volunteers, but since everyone is seeing different data samples with
  minimal overlap, the forum has little if any influence on votes.}
The result model represents a consensus among contributors, as to the
best that could be achieved with the available data and software.

>>>>

By coincidence, the typical escape velocity of massive galaxies is
such that $v_{\rm esc}^2/c^2$ is comparable to the apparent sizes of a
galaxies at cosmological distances.  This coincidence is fortunate,
because it makes the lensing deflection angle (which is $2v_{\rm
  esc}^2/c^2$) of distant galaxies comparable to their size on the
sky, and as a result, strong lensing by galaxies tends to produce
images that probe the dark halos of those galaxies.  This is
important, because while there is a general consensus that basic
mechanism of galaxy formation involve gravitational collapse,
fragmentation, and mergers of dark-matter clumps, into which gas fell,
cooling through radiative processes to form dense clouds and
eventually stars, there is much debate about the details \citep[for a
  summary, see][]{2012RAA....12..917S}.  In particular, the nature of
dark matter remains mysterious: most researchers take it to be a
collisionless non-relativistic fluid (cold dark matter or CDM) readily
studied by simulations \citep[for example, the influential millenium
  simulation by][]{2005Natur.435..629S}.  But other scenarios have
also been considered, such as a cold condensing boson fluid
\citep{2016ApJ...818...89S}, or dark matter particles with internal
degrees of freedom \citep{2010MNRAS.405...77S}, or not matter at all
but a modification of gravity \citep{2016PhRvL.117t1101M}.

@@

This paper continues by applying SpaghettiLens to lens-candidates
discovered through Space~Warps.  We present results from modelling of
56 of the 59 lens candidates reported by \cite{2016MNRAS.455.1191M}.
Each lens candidate was modelled in a collaborative refinement
process, where anyone interested can create a new model or modify an
existing model to try and make it better.\footnote{This is in contrast
  to the main Space~Warps project for discovering lenses, where
  volunteers in a crowd of $\gtrsim10^4$ make independent
  contributions.  Each person is presented with a random selection of
  survey-patches and invited to (in effect) vote on each.  The system
  estimates each volunteer's skill level according to test-patches
  interspersed with the real data, and weights their votes accordingly
  \citep{2016MNRAS.455.1171M}.  There is an active forum for
  volunteers, but since everyone is seeing different data samples with
  minimal overlap, the forum has little if any influence on votes.}
The result model represents a consensus among contributors, as to the
best that could be achieved with the available data and software.
